### 2019-11-12 latex/vhcs.tex
Finalized derivation of lagrangian for constrained dynamics

Take an underactuated mechanical system with Lagrangian
\begin{equation}\label{eqn:lagrangian}
\mathcal{L}(q,\dot{q}) = \frac{1}{2} \dot{q}^T D(q) \dot{q} - P(q)
\end{equation}
where \(q = (q_1,\ldots,q_n) \in \mathcal{Q}\) is the configuration vector, 
the inertia matrix \(D(q) = D^T(q)\) is positive definite for all 
\(q \in \mathcal{Q}\), and \(P(q)\) is the potential of the system.

@@

>>>>

\subsection{Review: Lagrangian Virtual Holonomic Constraints}
Take an underactuated mechanical system with Lagrangian
\begin{equation}\label{eqn:lagrangian}
\mathcal{L}(q,\dot{q}) = \frac{1}{2} \dot{q}^T D(q) \dot{q} - P(q)
\end{equation}
where \(q = (q_1,\ldots,q_n) \in \mathcal{Q}\) is the configuration vector, 
the inertia matrix \(D(q) = D^T(q)\) is positive definite for all 
\(q \in \mathcal{Q}\), and \(P(q)\) is the potential of the system.

@@

A natural question to ask is whether these constrained dynamics are also
Lagrangian. In fact, for VHCs applied to mechanical systems, the dynamics are
Euler-Lagrange. \cite{lagrangian_structure_reduced_dynamics_vhcs}

To see this, suppose the constrained dynamics had Lagrangian given by
\begin{equation*}
   \mathcal{L}_{\Psi}(s,\dot{s}) = \frac{1}{2}
   D_{\Psi}(s)\dot{s}^2 + V_{\Psi}(s)
\end{equation*}
where \(D_{\Psi} : \Theta \rightarrow \mathbb{R}_{>0}\) is the virtual mass
and \(V_{\Psi} : \Theta \rightarrow \mathbb{R}\) is the virtual potential of the
system. Then the equations of motion of this system are
\begin{equation*}
   D_{\Psi}'(s)\dot{s}^2 + D_{\Psi}(s)\ddot{s} - \frac{1}{2}D_{\Psi}'(s)\dot{s}
   + V_{\Psi}'(s) = 0
\end{equation*}
\begin{equation}\label{eqn:lagrangian_constrained_dynamics_general}
   \Rightarrow \ddot{s} = -\frac{V_{\Psi}'(s)}{D_{\Psi}(s)} -
   \frac{D_{\Psi}'(s)}{2 D_{\Psi}(s)}
\end{equation}

Setting (\ref{eqn:lagrangian_constrained_dynamics}) and
(\ref{eqn:lagrangian_constrained_dynamics_general}) equal to each other, one
can compute the values of \(D_{\Psi}\) and \(V_{\Psi}\). First, one sees that
\(V_{\Psi}(s)\) is defined by \(D_{\Psi}\) and \(\Psi_1\):
\begin{align*}
   \Psi_1(s) &= -\frac{V_{\Psi}'(s)}{D_{\Psi}(s)} \\
   \Rightarrow V_{\Psi}'(s) &= -D_{\Psi}(s) \Psi_1(s) \\
   \Rightarrow V_{\Psi}(s) &= - \int \limits_{0}^s
   D_{\Psi}(\tau)\Psi_1(\tau)d\tau
\end{align*}
where \(D_{\Psi}\) is given by
\begin{align*}
   \Psi_2(s) &= -\frac{D_{\Psi}'(s)}{D_\Psi(s)} \\
   \Rightarrow D_{\Psi}'(s) &= -D_{\Psi}(s) \Psi_2(s) \\
   \Rightarrow D_{\Psi}(s) &= \exp\left[ 
   -2\int \limits_{0}^s \Psi_2(\tau) d\tau \right]
\end{align*}

\subsection{Review: Hamiltonian Systems}
\textbf{TODO: What is a Hamiltonian system and why does it matter?}

One can compute the Hamiltonian of the Lagrangian (\ref{eqn:lagrangian}) by 
performing a Legendre transform on the Lagrangian. 
First, define the conjugate of momenta for \(q\) by 
\begin{equation*}
p = \frac{\partial \mathcal{L}}{\partial \dot{q}} \in \mathbb{R}^n
\end{equation*}
Then, the Legendre transform is performed by taking
\begin{equation*}
\mathcal{H}(q,p) = p^T \dot{q} - \mathcal{L}(q,\dot{q})
\end{equation*}
It is easy to verify that the Hamiltonian for system (\ref{eqn:lagrangian}) is 
given by the total mechanical energy (\ref{eqn:hamiltonian}).
\begin{equation}\label{eqn:hamiltonian}
\mathcal{H}(q,p) = E(q,p) = \frac{1}{2} p^T M^{-1}(q) p + V(q)
\end{equation}

The equations of motion for the system in Hamiltonian coordinates is given by
\begin{align}\label{eqn:hamiltionian_eom}
\begin{split}
\dot{q} &= \frac{\partial \mathcal{H}}{\partial p} = M^{-1}(q) p \\
\dot{p} &= -\frac{\partial \mathcal{H}}{\partial q} + B \tau
\end{split}
\end{align}

\textbf{Why bother looking at Hamiltonian systems? What is the intuition behind
these equations of motion?}

\subsection{Hamiltonian Virtual Nonholonomic Constraints}
